MassWateR: Improving quality control, analysis, and sharing of water quality data

### 2023-06-29 paper.Rmd
trying gt table, widths do not work on pdf

---
title: "MassWateR: Improving quality control, analysis, and sharing of water quality data"
date: "`r Sys.Date()`"
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Marcus W. Beck
    affiliation: Tampa Bay Estuary Program
    address:
    - 263 13th Ave S
    - St. Petersburg, Florida, USA 33701
    url: https://tbep.org
    orcid: 0000-0002-4996-0059
    email:  mbeck@tbep.org
  - name: Benjamen Wetherill
    url: https://www.acasak.com/
    email: bwetherill@acasak.co
    affiliation: ACASAK Consulting
    address:
    - Boston, Massachusetts, USA
    orcid: 0000-0002-0912-0225
  - name: Jillian Carr
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: Jillian.Carr@umb.edu
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
  - name: Pamela DiBona
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: pamela.dibona@state.ma.us
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(MassWateR)
library(flextable)
library(here)

@@

```{r}
filerequirements
```

>>>>

---
title: "MassWateR: Improving quality control, analysis, and sharing of water quality data"
date: "`r Sys.Date()`"
abstract: >
  An abstract of less than 150 words.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Marcus W. Beck
    affiliation: Tampa Bay Estuary Program
    address:
    - 263 13th Ave S
    - St. Petersburg, Florida, USA 33701
    url: https://tbep.org
    orcid: 0000-0002-4996-0059
    email:  mbeck@tbep.org
  - name: Benjamen Wetherill
    url: https://www.acasak.com/
    email: bwetherill@acasak.co
    affiliation: ACASAK Consulting
    address:
    - Boston, Massachusetts, USA
    orcid: 0000-0002-0912-0225
  - name: Jillian Carr
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: Jillian.Carr@umb.edu
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
  - name: Pamela DiBona
    url: https://www.mass.gov/orgs/massachusetts-bays-national-estuary-partnership
    email: pamela.dibona@state.ma.us
    affiliation: Massachusetts Bays National Estuary Partnership
    address:
    - University of Massachusetts Boston, 100 Morrissey Blvd
    - Boston, Massachusetts, USA 02125
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib
preamble: \usepackage{amsmath, booktabs, caption, longtable}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(MassWateR)
library(gt)
library(here)

@@

```{r, eval = knitr::is_html_output()}
filerequirements
```
```{r, eval = knitr::is_latex_output()}
filerequirements %>% tab_options(table.width = pct(90))
```

### 2023-06-29 paper.tex
trying gt table, widths do not work on pdf

The required data files for using are shown in table xx, including the steps in the workflow in Figure \ref{fig:workflow} when a file is required. The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section. These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential. Additionally, the \texttt{readMWRresultsview()} function\ldots{}

>>>>

The required data files for using \CRANpkg{MassWateR} are shown in table xx, including the files that apply to the workflow steps in Figure \ref{fig:workflow}. The files are each imported into R using specific \texttt{read} functions with relevant checks, explained in the next section. These checks verify multiple requirements outlined in the template files, with informative errors or warnings returned to the console to prompt the user on the required action to remedy a potential. Additionally, the \texttt{readMWRresultsview()} function\ldots{}

\begin{longtable}{llllll}
\toprule
Formatted file & Description & QC screening & QC reporting & WQX formatting & Data analysis \\ 
\midrule
Results & Water quality results organized by sample location and date & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> & <img src="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAMgAAAD8CAMAAAAFbRsXAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAACEUExURf////Pz89nZ2b29vaGhoYODg0lJSZeXl/v7+97e3sXFxaioqImJiWhoaDIyMgAAALi4uHx8fE5OTu3t7dLS0re3t21tbTY2NkFBQc3NzSIiIvj4+HV1dVhYWCYmJgwMDF9fX6+vrzw8POfn5xsbGxISEioqKn5+fpmZmVRUVBYWFgAAALm0mHMAAAAsdFJOU/////////////////////////////////////////////////////////8Ax9YJjAAAAAlwSFlzAAAOwwAADsMBx2+oZAAABp5JREFUeF7tnUFTKkEMhK3yRAm+AxexvFqF//8PPoRGWHYznYCbSSPfSSUsgcxkOplhfdJn8bxdvm3xiyKLzcty9f7vAP4mxXofArwBsMBjGny/g9UrXB+whEV5NtY7OPAKs9osG+8ArGFamg2cbfAC09oc05LNGyxrs4W3DWBZHDjb4BmWtfmAtzZfsKzNAt42gGVxeObVGFjP8NZmBcviwNsGMCzOEt7abGBZmzW8tREZWF9w1waGxeEiS2NgcZElMrBe4K4NDKsDb21EBhYVWSIDi4ssGFbnokkyRmRg0dQrMrD4TIdddWh9qyHeeUA0qkKHyIJddWjqVRlYTGRp9LEcIgt25YG7JhoNUl7fanTeHTNdovO+g4kslb1CJrLeYVeeTzhsobJXyESWzF4h/DWBWXlW8NdCpJqiqVelmqKbCDArD9tEUNEmbKariF4qslS0CdtEkDnHROrbT5iVh4ksmXNMRGTJLCGsvoVZfeCvhUrfhIksmSWEiSyVJYSJLJklhIksmNUH/lrILCGkvpVZQpjIgll9SOqVqUKIyFLpkNJNBJmZTkTWB8zqA4ctYFUfclJDRiyS1Ksz08kmgoxYJKlXpmV9NzOdiKx7mekyZSETWTIzndS3OjOd1Lewqg8RWTIznaRenZlONhFkZjpJvToznWwiwKo+RGTpzPT2JoKOeiciS+fL6XDYQKdOJ/UtrOpDRJZMR46ILJmjZWwT4V5mukzvnYksWAkAhw0eIiubuxFZ7U0EnXKK1Lcy5dRDZBWD1Lc6Iqu9iXA3IkvlmDWrb1W+W0jr20cnKxuyiQCr+txNfdsWWY/Umw4cNtBJvY9NhGL8kfr2kXqzISLrXlKvTsOB1Lf3clJDp+FADsnBqj5EZOncXBwOW8CqPn/kkJzOhjqpb2W22YjI0ilDyCE5mbXw8U2EYhCRJbMWktSrExAismTWQpJ6depCOGwhUxcSkSVTF7KZLrMWEpHV8wzQOjKqyUzvmXpfQncmISKrX490872R6R/XVe+psTisbX5NsTe36SRO1seJ667n2O2MYJbMmVfOscVSbxdxMhjtzrY5EVk9xMl+jp/wlaYs9eaLk80oieKBNuR2Runi5GeOn+EZ3Sz1JndO1pPlnUNZsJmeLE4s7YqHG5D6NlctPpvDnE5UdjujTHGyaAgl2sEhIitxLVy3t5JhZcFuZ5QnTtgQJ2MLViYwmx1Sn+5oj3EmspJ21Nm42APbSVjqzQnIht1A/0BrPSP1bYpaJHP8RGO6stSbsa3DPssTDe3KQjq/WuRz/AxzbDGRNXtAmAMXmJkHj5vMrRa9k+OIJcPZCjT7Ppsr6Z4zLfto6p1fLZJCaMT02CL1bcY+WzQkk2OE1bcp8j0aEjxtALtGinyPhmRigaYJHHYzEwzJRLWKR0yS5Hs0JHjaCSoMYDc7wZBcag0msvLqqWBILlMpq2/TAsL13gV4FqAfQ+IJ5WBIhrIJfzRJvXd9LCSDVYHVt7nd91hIzosSKrKSj8nFEtfZ2KLqObn7HqtKTtOXiqz07jte18dpuNBIzl1PjYiFBE/iIqvDWQ28so/j2MKvNukBCbYgUJRQkdXlICle28f+GVRk9QhIMCT7VY4uo50Oz+DVXXyPGZ4fUvenTrCOzoCdPX6y6XayF6/vYuPos3YKSKQFvPu0+Uzvd9Sa+3bik5ZTifXUiGj/tEm/42UOCRgB1+xDsOZt0TMg8c5QA1yxF/DidvoGJKhTWuB6/YAft9LpAOYZIZ1ig6t1JLIo2iT25EzY3pMLXKsrv7EoVghIuDc/Ba7UmdszcI2A/EIGxnW6c2sGrhKQmzMwLlOA2zJw6jZCm9syMC5SArh0FYUCclMGrvVPouk2lE2pgMQaQwOq/dfuqzNwsYA4DgFMU+9L0cGTjkfKBeTKDFzxW+r0HMAUBQNyVQauGJCrBFfy2QAnccFVMyBXTPeaAYkLruTTM36i071qQKKCq2xAooKrbkBi2z6FAxITXF0Oa7iBkw6K33rGL7hqB8SfgYsHxL/xXjwgbsHV5XxZDN8eQ/mAODOwQEB8GbjbcaYIjgzc7zhTBEcGhmV1aAbufzbAB9XAsKsPaTqW2WijtBfF0vL9gmZZIrAW/tAKiUbqPdIICSxEsENSsdnbwkpcEiLrHGstwcNCTC/vagNrx6Ti6nlr1auZaARXbb4TxilYogoZMxpcSkv6gIvT5oIT/chgmgi/j8E7kR1XB46jS25BH7Hefr29fhQMx9PTfxc0ivC3nJgvAAAAAElFTkSuQmCC" style="height:10px;"> \\ 
